Collapse Weddell and Check consistency

### 2023-09-18 WeddellSea_collapse.Rmd
Changes

@@

>>>>

source("R/functions.R")

@@

# Check Proportion of Stable Webs based on @Gross2009

```{r}
fwn <- c("BeagleChannel_links_original.csv",
                  "BurdwoodBank_links_original.csv",
                  "GulfSanJorge_links_original.csv",
                  "NorthernScotia_links_original.csv",
                  "SouthernScotia_links_original.csv",
                  "WeddellSea_links_original.csv")
fwn <- file.path("Data",fwn)
fw <- multiweb::readNetwork(fwn)

df_fw <- calc_topological_indices(fw)

df_fw <- df_fw %>% mutate(PSW=calculate_psw(Connectance,Size)$PSW)

ggplot(df_fw, aes(x = Connectance*Size, y = log(PSW))) +
  geom_point() +
  labs(x = "C * N", y = "PSW") +
  theme_classic()

node_to_remove <- "Euphausia superba"
node_index <- which(V(fw[[6]])$name == node_to_remove)
  food_web <- delete.vertices(fw[[6]], node_index)
calc_topological_indices(list(food_web,fw[[6]])) %>% mutate(PSW=calculate_psw(Connectance,Size)$PSW)
